Multilevel computation of glacier geometry \\ from Stokes dynamics

### 2021-05-27 paper/msg.tex
Minor: fiddle with glossary.

\renewcommand{\arraystretch}{1.1}
\begin{longtable}{l|ll}
\toprule
\textbf{Acronym} {\Large$\strut$} & \textbf{Definition} & \textbf{Reference} \\ \hline
CMB & climatic mass balance & Section \ref{sec:stokesgeometry} \\
FE & finite element & Section \ref{sec:fe} \\
IDO & ice dynamics operator & Section \ref{sec:weakido}, eqn.~\eqref{eq:ido} \\
IIGP & implicit ice geometry problem & Section \ref{sec:evolution} \\
MCD & multilevel constraint decomposition & Section \ref{sec:mcdstokes} \\
NCP & nonlinear complementarity problem & Section \ref{sec:stokesgeometry} \\
PNJ & projected, nonlinear Jacobi & Section \ref{sec:smoothers} \\
SIA & shallow ice approximation & Section \ref{sec:intro} \\
SIGP & steady ice geometry problem & Section \ref{sec:stokesgeometry}, eqn.~\eqref{eq:strongform} \\
SKE & surface kinematical equation & Section \ref{sec:stokesgeometry}, eqn.~\eqref{eq:ske} \\
VI & variational inequality & Section \ref{sec:weakido} \\
WU & work units & Section \ref{sec:mcdstokes} \\ % final \\ required
\bottomrule
\caption{Glossary of acronyms used in this paper.}
\label{tab:acronyms}
\end{longtable}

>>>>

\renewcommand{\arraystretch}{1.1}
\begin{longtable}{l|l|l}
\toprule
\textbf{Acronym} {\Large$\strut$} & \textbf{Definition} & \textbf{Reference} \\ \hline
CMB & climatic mass balance & Section \ref{sec:stokesgeometry} \\
FE & finite element & Section \ref{sec:fe} \\
IDO & ice dynamics operator & Section \ref{sec:weakido}, equation \eqref{eq:ido} \\
IIGP & implicit ice geometry problem & Section \ref{sec:evolution} \\
MCD & multilevel constraint decomposition & Section \ref{sec:mcdstokes}, Pseudocodes \ref{pc:mcdn-vcycle} and \ref{pc:mcdn-solver} \\
NCP & nonlinear complementarity problem & Section \ref{sec:stokesgeometry} \\
PNJ & projected, nonlinear Jacobi (smoother) & Section \ref{sec:smoothers}, Pseudocode \ref{pc:pnj} \\
SIA & shallow ice approximation & Section \ref{sec:intro} \\
SIGP & steady ice geometry problem & Section \ref{sec:stokesgeometry}, equation \eqref{eq:strongform} \\
SKE & surface kinematical equation & Section \ref{sec:stokesgeometry}, equation \eqref{eq:ske} \\
VI & variational inequality & Section \ref{sec:weakido} \\
WU & work units & Section \ref{sec:mcdstokes} \\ % final \\ required
\bottomrule
\caption{Glossary of acronyms used in this paper.}
\label{tab:acronyms}
\end{longtable}
